Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
more editing intro + contributions

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
{\em The first approach} uses a naive
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.
As it requires explicit unfolding up to a completeness
threshold, this approach may result in a state space explosion.
Instead of explicitly unfolding the dynamics, {\em the second approach} 
employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously.
Additionally, the second approach uses
abstraction refinement enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis
  from a transfer function representation into a state space
  representation.  This entails the verification of safety properties
  in addition to the already existing stability conditions which is a
  much harder problem.
%
\item We develop two approaches: the first, naive one relies on
  explicit unfolding of the system's dynamics up to a completeness
  threshold, whilst the second one is abstraction-based and leverages
  on the concept of abstraction refinement and acceleration to increase speed whilst retaining
  soundness.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

>>>>

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}.

{\em The first approach} uses a {\em naive}
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a {\em completeness threshold}, i.e.,
the number of iterations required to sufficiently unwind
the closed-loop state-space system such
that the boundaries are not violated for any larger number of iterations.
As it requires explicit unfolding up to the completeness
threshold, this approach may result in state space explosion.

Instead of explicitly unfolding the dynamics, {\em the second approach} 
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously and thus avoid
the state space explosion problem.
Additionally, the second approach uses
{\em abstraction refinement} enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis
  from a transfer function representation into a state space
  representation.  This entails the verification of safety properties
  in addition to the already existing stability conditions which is a
  much harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase speed whilst retaining
  soundness.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}
